\begin{itemize}
\item \verb|ERROR ! Unsupported Keyword !|

The program stops because unsupported keyword is specified.

\item \verb|"ERROR !  Keyword| \textit{keyword} \verb|is duplicated !|

The program stops because a parameter is specified twice.

\item \verb|ERROR ! Unsupported Solver : | \textit{solver} \vspace{-0.3cm}
\item \verb|ERROR ! Unsupported Model : | \textit{model} \vspace{-0.3cm}
\item \verb|Sorry, this system is unsupported in the STANDARD MODE...| \\
  \verb|Please use the EXPART MODE, or write a NEW FUNCTION and post it us.|

The program stops because unsupported parameter for 
\verb|method|, \verb|model|, or \verb|lattice|
is specified.

\item \verb#ERROR ! abs(2 * Sz) > nsite in Hubbard model !# \vspace{-0.3cm}
\item \verb#ERROR ! Nelec > 2 * nsite in Hubbard model !#\vspace{-0.3cm}
\item \verb#ERROR ! (nelec + 2 * Sz) % 2 != 0 in Hubbard model !#\vspace{-0.3cm}
\item \verb#ERROR ! nelec <= nsite && 2 * |Sz| > nelec in Hubbard model !#\vspace{-0.3cm}
\item \verb#ERROR ! nelec > nsite && 2 * |Sz| > 2 * nsite - nelec in Hubbard model !#\vspace{-0.3cm}
\item \verb#ERROR ! abs(2 * Sz) > nsite in Spin model !#\vspace{-0.3cm}
\item \verb#ERROR ! (nsite + 2 * Sz) % 2 != 0 in Spin model !#\vspace{-0.3cm}
\item \verb#ERROR ! abs(2 * Sz) > nsite in Hubbard model !#\vspace{-0.3cm}
\item \verb#ERROR ! Nelec_cond / 2 + Nelec_loc > nsite in Kondo model !#\vspace{-0.3cm}
\item \verb#ERROR ! (nelec_cond + nelec_loc + 2 * Sz) % 2 != 0 in Kondo model !#\vspace{-0.3cm}
\item \verb#ERROR ! nelec_cond <= nsite / 2 && 2 * |Sz| > nelec_cond + nelec_loc ...#\vspace{-0.3cm}
\item \verb#ERROR ! nelec_cond > nsite / 2 && abs(Sz2) > nsite / 2 * 3 - nelec...#

In the calculation of the canonical ensemble, 
there are some irrelevant combinations of the number of electrons, the number of sites, and the total spin moment
( the number of electrons is larger twice than the number of sites);
If these situations are detected, the program will stop.

\item \verb|Check ! |\textit{keyword} \verb| is SPECIFIED but will NOT be USED.|\\
      \verb|        Please COMMENT-OUT this line|\\
      \verb|        or check this input is REALLY APPROPRIATE for your purpose !|

Because an unnecessary parameter is specified, the program suggests checking the input file.
If that parameter is actually unnecessary, please delete or comment out this line.

\item \verb|ERROR ! |\textit{keyword}\verb| is NOT specified !|

The program stops because a prerequisite keyword is not specified.

\item \textit{keyword} \verb|=| \textit{value} \verb|######  DEFAULT VALUE IS USED  ######|

This is not an error message.
The program states that the default value is used because this keyword is not specified.

\end{itemize}
